Model Finding for Recursive Functions in SMT

### 2015-04-30 tex/main.tex
Minor

In the remainder of the section, we fix a signature $\Sigma$.
Say that $\Sigma$-formula $\varphi$ is well-defined with respect to functions $\sfundefs{\Sigma}$, 
and the definitions in $\sfundefs{\Sigma}$ are logically consistent.
We may translate $\varphi$ into a equisatisfiable formula $\psi$ for which known model-finding procedures~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} are applicable.
In particular, this section presents a method for constructing an extended signature $\extendsig{ \Sigma }$,
and a $\extendsig{ \Sigma }$-formula $\psi$ such that $\varphi$ and $\psi$ are equisatisfiable.
The intuition behind this translation is use an uninterpreted type to abstract the set of \emph{relevant} tuples for each recursive function $f$,
and restrict the quantification of the function definition for $f$ to a variable of this type.
Informally, the relevant tuples $\vec t$ of a function $f$ are the ones for which the interpretation of $f( \vec t )$ is relevant to the satisfiability of $\varphi$.

>>>>

In the remainder of the section, we fix a signature $\Sigma$.
Say that $\Sigma$-formula $\varphi$ is well-defined with respect to functions $\sfundefs{\Sigma}$, 
and the definitions in $\sfundefs{\Sigma}$ are logically consistent.
%We may translate $\varphi$ into a equisatisfiable formula $\psi$ for which known model-finding procedures~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} are applicable.
This section presents a method for constructing an extended signature $\extendsig{ \Sigma }$,
and a $\extendsig{ \Sigma }$-formula $\psi$ such that $\varphi$ and $\psi$ are equisatisfiable.
The intuition behind this translation is use an uninterpreted type to abstract the set of \emph{relevant} tuples for each recursive function $f$,
and restrict the quantification of the function definition for $f$ to a variable of this type.
Informally, the relevant tuples $\vec t$ of a function $f$ are the ones for which the interpretation of $f( \vec t )$ is relevant to the satisfiability of $\varphi$.
